The importance of measurement uncertainty in ecological management

### 2018-02-01 manuscripts/manuscript.Rmd
fixing typos

abstract: |
  Ecological management and decision-making typically focus on uncertainty about the future, but surprisingly little is known about how to account for uncertainty of the present: that is, the realities of having only partial or imperfect measurements.  Our two primary paradigms for handling decisions under uncertainty -- the precautionary principle and optimal control -- have so far given entirely controdictory results.  This paradox is best illustrated in the example of fisheries management, where many ideas that guide our thinking about ecological decision making were first developed.  There, we find that simplistic optimal control approaches have repeatedly concluded that a manager should increase catch quotas when faced with greater uncertainty about the standing stock biomass.  Meanwhile, most current best practices take a more precautionary approach, decreasing catch quotas by a fixed amount to account for uncertainty.  Using comparisons to both simulated and historical catch data, we find that neither approach is sufficient to avoid stock collapses under moderate observational uncertainty.  Using cutting-edge point-based partially observed Markov decision process (POMDP) methods, we demonstrate how this paradox arises from flaws in the standard management theory, which contributes to over-exploitation of fisheries and increased probability of economic and ecological collapse.  In contrast, we find POMDP-based management avoids such over-exploitation while also generating higher economic value through adaptive learning.  These results have significant implications for how we handle uncertainty in both fisheries and ecological management more generally.  Dealing with uncertainty in decisions requires approaches which are both adaptive and explicit about uncertainty, such as POMDPs.

>>>>

abstract: |
  Ecological management and decision-making typically focus on uncertainty about the future, but surprisingly little is known about how to account for uncertainty of the present: that is, the realities of having only partial or imperfect measurements.  Our two primary paradigms for handling decisions under uncertainty -- the precautionary principle and optimal control -- have so far given entirely contradictory results.  This paradox is best illustrated in the example of fisheries management, where many ideas that guide our thinking about ecological decision making were first developed.  There, we find that simplistic optimal control approaches have repeatedly concluded that a manager should increase catch quotas when faced with greater uncertainty about the standing stock biomass.  Meanwhile, most current best practices take a more precautionary approach, decreasing catch quotas by a fixed amount to account for uncertainty.  Using comparisons to both simulated and historical catch data, we find that neither approach is sufficient to avoid stock collapses under moderate observational uncertainty.  Using cutting-edge point-based partially observed Markov decision process (POMDP) methods, we demonstrate how this paradox arises from flaws in the standard management theory, which contributes to over-exploitation of fisheries and increased probability of economic and ecological collapse.  In contrast, we find POMDP-based management avoids such over-exploitation while also generating higher economic value through adaptive learning.  These results have significant implications for how we handle uncertainty in both fisheries and ecological management more generally.  Dealing with uncertainty in decisions requires approaches which are both adaptive and explicit about uncertainty, such as POMDPs.

### 2018-02-01 manuscripts/manuscript.tex
fixing typos

  \begin{abstract}
  Ecological management and decision-making typically focus on uncertainty
  about the future, but surprisingly little is known about how to account
  for uncertainty of the present: that is, the realities of having only
  partial or imperfect measurements. Our two primary paradigms for
  handling decisions under uncertainty -- the precautionary principle and
  optimal control -- have so far given entirely controdictory results.
  This paradox is best illustrated in the example of fisheries management,
  where many ideas that guide our thinking about ecological decision
  making were first developed. There, we find that simplistic optimal
  control approaches have repeatedly concluded that a manager should
  increase catch quotas when faced with greater uncertainty about the
  standing stock biomass. Meanwhile, most current best practices take a
  more precautionary approach, decreasing catch quotas by a fixed amount
  to account for uncertainty. Using comparisons to both simulated and
  historical catch data, we find that neither approach is sufficient to
  avoid stock collapses under moderate observational uncertainty. Using
  cutting-edge point-based partially observed Markov decision process
  (POMDP) methods, we demonstrate how this paradox arises from flaws in
  the standard management theory, which contributes to over-exploitation
  of fisheries and increased probability of economic and ecological
  collapse. In contrast, we find POMDP-based management avoids such
  over-exploitation while also generating higher economic value through
  adaptive learning. These results have significant implications for how
  we handle uncertainty in both fisheries and ecological management more
  generally. Dealing with uncertainty in decisions requires approaches
  which are both adaptive and explicit about uncertainty, such as POMDPs.
  \end{abstract}
   \begin{keyword} Measurement uncertainty \sep POMDP \sep Decision theory \sep Fisheries \sep Conservation \sep \end{keyword}
 \end{frontmatter}

@@

Our results also have important consequences for ecological management
more generally. The study and application of management strategies such
as MSY and CE underpin much of conservation and natural resource
management in forest management and many other terrestrial ecosystems
(e.g. Clark and Mangel 2000). Descision making under uncertainty is a
central challenge for ecology and conservation biology (Polasky et al.
2011), which we have long attempted to address through either simplified
optimal control models or more heuristic approaches such as the
precautionary principle and resilience thinking (Fischer et al. 2009).
We have illustrated how both of these approaches can fail to provide an
adequate strategy when faced with measurement uncertainty. To avoid this
pitfall, a strategy must be dynamic to make best use of the available
information without assuming that information is perfect. The
simplisitic optimal control approach of CE fails by placing too much
confidence in measurements even when they are significantly at odds with
prior expectations. Similarly, the TAC approach also fails due to it's
reliance on a simple one-size-fits-all strategy, not reducing catch
quotas sufficiently when stocks are too low but also failing to increase
them when stocks are higher. It is precisely this ability to adapt the
policy in response to available information, as illustrated in Figure
\ref{policy}, that makes the POMDP approach successful. Nevertheless, it
may be tempting to see these results as either trivial or impractical,
but a closer inspection reveals they are neither.

>>>>

  \begin{abstract}
  Ecological management and decision-making typically focus on uncertainty
  about the future, but surprisingly little is known about how to account
  for uncertainty of the present: that is, the realities of having only
  partial or imperfect measurements. Our two primary paradigms for
  handling decisions under uncertainty -- the precautionary principle and
  optimal control -- have so far given entirely contradictory results.
  This paradox is best illustrated in the example of fisheries management,
  where many ideas that guide our thinking about ecological decision
  making were first developed. There, we find that simplistic optimal
  control approaches have repeatedly concluded that a manager should
  increase catch quotas when faced with greater uncertainty about the
  standing stock biomass. Meanwhile, most current best practices take a
  more precautionary approach, decreasing catch quotas by a fixed amount
  to account for uncertainty. Using comparisons to both simulated and
  historical catch data, we find that neither approach is sufficient to
  avoid stock collapses under moderate observational uncertainty. Using
  cutting-edge point-based partially observed Markov decision process
  (POMDP) methods, we demonstrate how this paradox arises from flaws in
  the standard management theory, which contributes to over-exploitation
  of fisheries and increased probability of economic and ecological
  collapse. In contrast, we find POMDP-based management avoids such
  over-exploitation while also generating higher economic value through
  adaptive learning. These results have significant implications for how
  we handle uncertainty in both fisheries and ecological management more
  generally. Dealing with uncertainty in decisions requires approaches
  which are both adaptive and explicit about uncertainty, such as POMDPs.
  \end{abstract}
   \begin{keyword} Measurement uncertainty \sep POMDP \sep Decision theory \sep Fisheries \sep Conservation \sep \end{keyword}
 \end{frontmatter}

@@

Our results also have important consequences for ecological management
more generally. The study and application of management strategies such
as MSY and CE underpin much of conservation and natural resource
management in forest management and many other terrestrial ecosystems
(e.g. Clark and Mangel 2000). Decision making under uncertainty is a
central challenge for ecology and conservation biology (Polasky et al.
2011), which we have long attempted to address through either simplified
optimal control models or more heuristic approaches such as the
precautionary principle and resilience thinking (Fischer et al. 2009).
We have illustrated how both of these approaches can fail to provide an
adequate strategy when faced with measurement uncertainty. To avoid this
pitfall, a strategy must be dynamic to make best use of the available
information without assuming that information is perfect. The
simplistic optimal control approach of CE fails by placing too much
confidence in measurements even when they are significantly at odds with
prior expectations. Similarly, the TAC approach also fails due to it's
reliance on a simple one-size-fits-all strategy, not reducing catch
quotas sufficiently when stocks are too low but also failing to increase
them when stocks are higher. It is precisely this ability to adapt the
policy in response to available information, as illustrated in Figure
\ref{policy}, that makes the POMDP approach successful. Nevertheless, it
may be tempting to see these results as either trivial or impractical,
but a closer inspection reveals they are neither.
